---
title       : Intercept and slope of Linear Regression
subtitle    : The relation of intercept, slope and mean of data
author      : Helen Gu, Teacher of Shanghai Sports Institute
job         : Shanghai Sports Institute
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
## Summary of the Problem
Suppose we have data of x and y. Are the following two linear regression the same?

Case 1

lm(I(y - mean(y)) ~ I(x - mean(x)) - 1)

Case 2

X1 <- (x - mean(x))/sd(x)

Y1 <- (y - mean(y))/sd(y)

lm(Y1 ~ X1)

---
## Example1
```{r, echo=FALSE}
set.seed(3)
```
```{r, echo=TRUE}
x=c(1:10)
y=1+5*runif(10)+x
```
```{r, echo=FALSE, fig.height=6.2, fig.width=6}
plot(y-mean(y), x-mean(x), col="orange", main="Example1")
M1<-lm(I(y - mean(y)) ~ I(x-mean(x))  -1 )
abline(M1,col= "pink")
X1 <- (x - mean(x))/sd(x)
Y1 <- (y - mean(y))/sd(y)
points(Y1,X1, col= "blue")
M2<-lm(Y1~X1)
abline(M2,col= "purple")
legend("topright", lty=1, col=c("pink","purple"), legend=c("lm((y-mean(y))~(x-mean(x))-1)", "lm(Y1~X1)"))
```

---
## Example2
```{r, echo=FALSE}
set.seed(3)
```
```{r, echo=TRUE}
x=c(1:10)
y=1+10*runif(10)+x
```
```{r, echo=FALSE, fig.height=6.2, fig.width=6}
plot(y-mean(y), x-mean(x), col="orange", main="Example2")
M1<-lm(I(y - mean(y)) ~ I(x-mean(x))  -1 )
abline(M1,col= "red")
X1 <- (x - mean(x))/sd(x)
Y1 <- (y - mean(y))/sd(y)
points(Y1,X1, col= "blue")
M2<-lm(Y1~X1)
abline(M2,col= "navy")
legend("topright", lty=1, col=c("red","navy"), legend=c("lm((y-mean(y))~(x-mean(x))-1)", "lm(Y1~X1)"))
```

---
## Conclusion
From the Examples, 
- the intercept of two cases are the same, they all equal 0.

- the slope of two cases are different. The difference is depend on sd(x)/sd(y). Because relation of the slope of case 2 ($k_{2}$) and case 1 ($k_{1}$) is $k_{2}$=$\frac{sd(x)}{sd(y)}\times$$k_{1}$.

